Legacy Data Confounds Genomics Studies

### 2018-12-20 legacy.tex
new figures

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_NORepeat_SNPs.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_NORepeat_Indels.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_Repeat_SNPs.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_Repeat_Indels.jpg}

>>>>

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_NonRepeatSNPs.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_NonRepeatIndels.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_RepeatSNPs.jpg}

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_RepeatIndels.jpg}
